Cluster Analysis: Identifying Parkinson's Disease Subtypes

### 2015-06-24 writeup/parkinsons.tex
add brief description of summary plots
k = 4!!!!

>>>>

\subsubsection{Cluster summaries}

Available in
Figures~\ref{fig:kmeans-summaries-2},~\ref{fig:kmeans-summaries-3},
and~\ref{fig:kmeans-summaries-4}. Error bar is standard error.

\subsubsection{Interpretation}

$k = 2$ seems too basic. Cluster is organized solely by severity - all
symptoms, including motor and nonmotor, are higher in severity in cluster 1,
and lower in cluster 2. Quite consistently, groups in cluster 1 are generally
of slightly higher age and pd duration.

$k = 3$ seems like a further development of $k = 2$, where clusters are simply
organized by linearly increasing severity.

$k = 4$ is where it gets interesting.
